\documentclass{article}

% Macros to make this problem look like the rest of our problems.
\usepackage{icpc_problem}

% Title of your problem.
\title{A: Bumper-to-Bumper Traffic}

% Who made the problem
\author{Darko Aleksic}

% Keywords, from a set of standard keywords.
\keywords{simple}

% Anything you want to say about the problem, including how one could solve it
\comments{Two cars in a lane changing speeds - will they ever collide?
}

% Difficulty on a 1..10 scale.
\difficulty{1}

\begin{document}

\begin{problemDescription}
It's the slow crawl of rush hour. At any point of time, each vehicle is either 
stopped or is moving at the extremely slow speed of 1 meter per second. Lately, 
vehicles come equipped with a simple ``black box" that records all changes in a 
vehicle's speed. In this problem, speeds change instantaneously.  The road is 
modelled as the real line (units in meters). So a car is identified by its 
position on the line.  Also, cars are 4.4 meters long.

Given initial positions of two cars that are driving along the real line in 
the positive direction and a transcript of their speed changes, do these cars 
ever collide? While such a collision would be very slow speed (a "bumper tap''), 
any collision could result in erroneous readings from the black box in the 
future, so the portions of the transcripts after a collision might not make sense.
Both cars continue indefinitely after their last recorded speed change.
\end{problemDescription}

\begin{inputDescription}
Input may consist of multiple cases.  Each case is described on three lines.
Spacing of the data is arbitrary.
The first line contains two integers $0 <= x_{1},x_{2} <= 20$ indicating the 
initial positions of the rears of the two vehicles in meters. You are guaranteed 
that either $x_{1} + 5 <= x_{2}$ or $x_{2} + 5 <= x_{1}$.  Initially (at time 0), 
the two cars are stopped.  

The second line begins with 
a number $0 <= n_{1} <= 10$ indicating the number of times the speed of the first
car changes. The rest of the line contains $n_{1}$ integers $0 < t_{1} < t_{2} < 
 ... < t_{n_{1}} <= 10$ indicating the times (in seconds) at which the first vehicle 
changes speeds. So at time $t_{1}$ it begins driving 1 m/s, at time $t_{2}$ it 
stops, at time $t_{3}$ it begins driving 1 m/s, and so on.  The third line 
is laid out the same way, but for the second car.  The number of starts and
stops may be different.  Following the final case is a line containing two 0's.
\end{inputDescription}

\begin{outputDescription}
For each case, display the case number followed by the answer, formatted as in
the sample.  If the vehicles collide, output the message ``bumper tap at time 
$s$" on a single line where $s$ is the number of seconds from time 0 that the 
vehicles first collide, rounded up to the nearest second. If the vehicles do 
not collide, output the message ``safe and sound".

\end{outputDescription}

\begin{sampleInput}
0 5
3 1 4 5
3 1 4 6
0 5
3 1 4 5
3 1 4 5
2 13
1 1
3   4   7   10
0 0
\end{sampleInput}
\begin{sampleOutput}
Case 1: bumper tap at time 6
Case 2: safe and sound
Case 3: safe and sound
\end{sampleOutput}

\end{document}
