\documentclass{article}

% Macros to make this problem look like the rest of our problems.
\usepackage{icpc_problem}

% Title of your problem.
\title{F: Flow Shop}

% Who made the problem
\author{Darko Aleksic}

% Keywords, from a set of standard keywords.
\keywords{simple}

% Anything you want to say about the problem, including how one could solve it
\comments{Picture a block of cheese and a deranged chef with a long straight 
knife stops along two sides.}

% Difficulty on a 1..10 scale.
\difficulty{1}

\begin{document}

\begin{problemDescription}
Sean's Swathers makes custom swathers (equipment used to harvest grain). All swathers 
go through the same basic stages in their construction: for example they all need 
to have a cutting bar, a grain belt, and a reel fitted. However, these components can 
be customized based on the buyer's needs, so these various stages may take different 
amounts of time between different swathers.

In particular, $n$ swathers have been ordered and there are $m$ stages in the 
manufacturing process. The swathers will each go through the same sequence of 
stages. In particular, the processing occurs as follows.  For each swather $j$
and each stage $i$, it takes $p_{j,i}$ units of time to complete stage $i$ for 
swather $j$. The workers at each stage may only work on one swather at a time. 
At the start of the day all swather orders are ready to be processed by the first 
stage. At any point in the process, if the workers at stage $i$ are idle and there
are swathers waiting to be processed at this stage, then the workers will pick 
the swather that has the lowest label (they are labelled from $1$ to $n$).
Determine the time each swather is completed.
\end{problemDescription}

\begin{inputDescription}
Input may consist of multiple cases. A case begins with a single line containing 
$n$ and $m$ $(1 <= n,m <= 1000)$, representing the number of swathers and stages 
(respectively). 
Following this are $n$ lines, each with $m$ integers. The $i$’th integer of the 
$j$’th line is $p_{j,i}$, giving the amount of time it will take for the workers 
at stage $i$ to complete swather $j$  $(1 <= p_{j,i} <= 10)$.  The last case is followed
by a line containing 0 0 (zeroes).  There may be blank lines for readability.
\end{inputDescription}

\begin{outputDescription}
For each case, display the case number followed by a single line containing $n$
integers $c_{1}$ $c_{2}$ ... $c_{n}$ with a single space between consecutive integers.
These should be such that stage $m$ for swather $j$ is completed at time $c_{j}$.
Format as in the sample.
\end{outputDescription}

\begin{sampleInput}
2 3
1 2 3
3 2 1

3 2
3 1
4 7
2 5

0 0
\end{sampleInput}
\begin{sampleOutput}
Case 1: 6 7
Case 2: 4 14 19
\end{sampleOutput}

\end{document}
