\documentclass{article}

% Macros to make this problem look like the rest of our problems.
\usepackage{icpc_problem}

% Title of your problem.
\title{H: Corrupted Gradebook}

% Who made the problem
\author{Ryan Patrick}

% Keywords, from a set of standard keywords.
\keywords{simple}

% Anything you want to say about the problem, including how one could solve it
\comments{
knife stops along two sides.}

% Difficulty on a 1..10 scale.
\difficulty{1}

\begin{document}

\begin{problemDescription}
A gradebook has been corrupted so that the columns have been removed. Each 
student's record simply contains a single string of digits. Knowing that the 
string of digits must have come from $n$ different assignments (each with a 
possible integer grade between 0 and 100, inclusive), parse the string so that 
the average of the $n$ grades is maximized. 
\end{problemDescription}

\begin{inputDescription}
Input may consist of multiple cases, with each having a one line description. 
The line will contain an integer from 1 to 25 representing the number of
grades.  After some white space there will be a string of digits.  This is the 
string to parse into the (optimal) original grades.  The last case is followed 
by a line with two 0's (zeroes).

When correctly parsed, none of the grades will have leading 0's (zeroes), though
individual grades may have value of 0, each shown simply as '0'.
\end{inputDescription}

\begin{outputDescription}
For each case, display the case number followed by the optimal average grade,
rounded to the nearest integer.  Format as in the sample.
\end{outputDescription}

\begin{sampleInput}
2  835
2  100
1  100
0  0
\end{sampleInput}
\begin{sampleOutput}
Case 1: 44
Case 2: 5
Case 3: 100
\end{sampleOutput}

\end{document}
